The Inconsistency in G\"odel's Ontological Argument: \\ A Success Story for AI in Metaphysics

### 2016-02-02 Papers/InProgress/IJCAI/submission.tex
paper has now exactly 6 pages plus references as required

For a computational analysis of G\"odel's ontological argument, the embedding of HOMLs such as \textbf{K},
\textbf{KB} and \textbf{S5} with various domain conditions (possibilist and actualist quantification)
is required. This idea has been successfully employed in related work
\cite{C40}. The embedding of HOML is in fact
straightforward. Formulas in HOML are \emph{lifted}, i.e., converted into predicates
over worlds, which are themselves explicitly represented as
terms. The logical constants of HOML are translated to HOL terms in such a way that, for instance, 
%$\neg \varphi$, $\varphi\vee\psi$
$\Box \varphi$ and $\Diamond \varphi$ (relative to a current world
$w_o$) are mapped, respectively, to the HOL formulas
$\forall w. (r w_0 w) \imp (\varphi w)$ and
$\exists w. (r w_0 w) \wedge (\varphi w)$. This form of embedding is
precisely the well-known standard translation
\cite{DBLP:journals/logcom/Ohlbach91}, which is here intra-logically
realized --- and extended for quantifiers --- in HOL by stating a set
of equations defining the logical constants (Fig.~\ref{QML_S5U}). The
resulting object logic is the HOML \textbf{K} with rigid terms and constant
domains (possibilist quantifiers). Other logics (e.g. \textbf{KB}, \textbf{S5}) can be
embedded by adding axioms that restrict the accessibility relation
$r$. Varying domains and actualist quantifiers can be simulated by using
 an existence predicate to guard the
quantifiers. The embedding approach is, therefore, very flexible.

\subsection{Improved Embedding}\label{sec:improvedembedding}
\begin{figure}[t]
\centerline{\includegraphics[width=1\columnwidth]{./Images/QML_S5U.png}}
\caption{Improved Embedding of \SFiveU} \label{QML_S5U}
\end{figure}

@@

%\section*{Acknowledgments} Will be added at a later point.
%\paragraph*{Acknowledgments} Will be added at a later point.

>>>>

For a computational analysis of G\"odel's ontological argument, the embedding of HOMLs such as \textbf{K},
\textbf{KB} and \textbf{S5} with various domain conditions (possibilist and actualist quantification)
is required. This idea has been successfully employed in related work
\cite{C40}. The embedding of HOML is in fact
straightforward. Formulas in HOML are \emph{lifted}, i.e., converted into predicates
over worlds, which are themselves explicitly represented as
terms. The logical constants of HOML are translated to HOL terms in such a way that, for instance, 
%$\neg \varphi$, $\varphi\vee\psi$
$\Box \varphi$ and $\Diamond \varphi$ (relative to a current world
$w_o$) are mapped, respectively, to the HOL formulas
$\forall w. (r w_0 w) \imp (\varphi w)$ and
$\exists w. (r w_0 w) \wedge (\varphi w)$. This form of embedding is
precisely the well-known standard translation
\cite{DBLP:journals/logcom/Ohlbach91}, which is here intra-logically
realized --- and extended for quantifiers --- in HOL by stating a set
of equations defining the logical constants (Fig.~\ref{QML_S5U}). The
resulting object logic is the HOML \textbf{K} with rigid terms and constant
domains (possibilist quantifiers). Other logics (e.g. \textbf{KB}, \textbf{S5}) are
embedded by adding axioms that restrict the accessibility relation
$r$. Varying domains and actualist quantifiers can be simulated by using
 an existence predicate to guard the
quantifiers. The embedding approach is, therefore, very flexible.

\subsection{Improved Embedding}\label{sec:improvedembedding}
\begin{figure}[t]
\centerline{\includegraphics[width=1\columnwidth,height=10cm]{./Images/QML_S5U.png}}
\caption{Improved Embedding of \SFiveU} \label{QML_S5U}
\end{figure}

@@

%\section*{Acknowledgments} Will be added at a later point.
\paragraph*{Acknowledgments} Will be added at a later point.
